\tool: Revisiting BadUSB with Type-C

### 2021-03-22 WOOT/Files/discussion.tex
edits. `
full control mode

\subsection{Limitation}
There exist multiple limitations of \tool. To begin with, when \tool is attached, the victim's device may not be set to mirror the screen. 
Depending on the victim's settings, the \tool may be used as an extended monitor or be set to `Desktop Mode' or not be enabled at all. Though we proposed the attack initialization in Section~\ref{subsec:attack_init} to inject keystrokes to ensure \tool is mirroring primary screen. But without knowing the exact operating system of the victim's device, \tool may have to try multiple injections before successfully mirroring the screen.
Moreover, as mentioned in Section~\ref{sec:experiment}, \tool cannot directly obtain the information on the lock screen.
 Apart from that, we also noticed that in most devices, when an external monitor is connected to the device, there will be notifications about the monitor. In iPad, there is a small blue icon on the notification bar. In Windows 10, there is a pop-up for user to select the functionality of the external monitor. In latter case of a pop-up, \tool can dismiss it by injecting keystrokes as described in Section~\ref{subsec:attack_init}. But they are still noticeable by the victim. Also, it cannot be ignored that DisplayPort over \ac{USB} is not available on all devices. When selecting devices to test \tool, we find that many smartphones equipped with USB-C connectors actually do not support \ac{USB} 3.x protocol. There is a incomplete list of devices that support DisplayPort over \ac{USB}~\cite{usbclist}. Most vendors like HUAWEI and Samsung tend to support \ac{USB} 3.x protocol in their \mbox{high-end} smartphones. But there also exists vendor like Xiaomi who does not support \ac{USB} 3.x protocol at all.

>>>>

\subsection{Limitation}
There exist multiple limitations of \tool. To begin with, when \tool is attached, the victim's device may not be set to mirror the screen.
Depending on the victim's settings, the \tool may be used as an extended monitor or be set to `Desktop Mode' or not be enabled at all. Though we proposed the attack initialization in Section~\ref{subsec:attack_init} to inject keystrokes to ensure \tool is mirroring primary screen. But without knowing the exact operating system of the victim's device, \tool may have to try multiple injections before successfully mirroring the screen.
Moreover, as mentioned in Section~\ref{sec:experiment}, \tool cannot directly obtain the information on the lock screen.
 Apart from that, we also noticed that in most devices, when an external monitor is connected to the device, there will be notifications about the monitor. In iPad, there is a small blue icon in the notification bar. In Windows 10, there is a pop-up for user to select the functionality of the external monitor. In latter case of a pop-up, \tool can dismiss it by injecting keystrokes as described in Section~\ref{subsec:attack_init}. But they are still noticeable by the victim. Also, it cannot be ignored that DisplayPort over \ac{USB} is not available on all devices. When selecting devices to test \tool, we find that many smartphones equipped with USB-C connectors actually do not support \ac{USB} 3.x protocol. There is an incomplete list of devices that support DisplayPort over \ac{USB}~\cite{usbclist}. Most vendors like HUAWEI and Samsung tend to support \ac{USB} 3.x protocol in their \mbox{high-end} smartphones. But there also exists vendor like Xiaomi who does not support \ac{USB} 3.x protocol at all.

### 2021-03-22 WOOT/Files/introduction.tex
full control mode

Moreover, we implemented multiple attacking
modes of \ac{USB} attacks based on our approach to verify its effectiveness,
including \ac{HID} Emulator Mode, Video Capture Mode, and Full Control Mode.  To improve the
efficiency and performance of \tool, we designed a filtering algorithm to
preprocess the video data before network transmission.  
We conducted
a series of experiments for each attack mode as well as for different types of
devices, including smartphones, personal computers, and tablet computers, to
validate the usability of \tool.  We also conducted a case study for attacks in
sharing power banks, one of the application scenarios of \tool.  
After the validation of our attack model, we
proposed several defense methods as countermeasures, including external
hardware authorization, distrust-by-default, etc.  It is worth noting that we
designed a method, called isolated \ac{UI} rendering, to separate the user interface
into sensitive and insensitive layers.  Only the insensitive layer's content would be passed to the insecure driver and thus rendered on the external display, protecting the sensitive layer's content.
%\shuqing{Case study, evaluation, notable results.}

>>>>

Moreover, we implemented multiple attacking
modes of \ac{USB} attacks based on our approach to verify its effectiveness,
including \ac{HID} Emulator Mode, Video Capture Mode, and full control mode  To improve the
efficiency and performance of \tool, we designed a filtering algorithm to
preprocess the video data before network transmission.
We conducted
a series of experiments for each attack mode as well as for different types of
devices, including smartphones, personal computers, and tablet computers, to
validate the usability of \tool.  We also conducted a case study for attacks in
sharing power banks, one of the application scenarios of \tool.
After the validation of our attack model, we
proposed several defense methods as countermeasures, including external
hardware authorization, distrust-by-default, etc.  It is worth noting that we
designed a method, called isolated \ac{UI} rendering, to separate the user interface
into sensitive and insensitive layers.  Only the insensitive layer's content would be passed to the insecure driver and thus rendered on the external display, protecting the sensitive layer's content.
%\shuqing{Case study, evaluation, notable results.}
